---
title: "Journal (reproducible report)"
author: "Pawin Traitrongsat"
date: "2020-11-28"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Challange 1

Last compiled: `r Sys.Date()`

## Challange 1.1
```{r, fig.width=10, fig.height=7}
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

bike_orderlines_joined_tbl <- orderlines_tbl %>%
        left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
        left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
        
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
 separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
  
bike_orderlines_wrangled_cs_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ",") 

sales_by_cs_tbl <- bike_orderlines_wrangled_cs_tbl %>%
  select(order_date, state, city, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(state, city) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))    
    
sales_by_cs_tbl %>%
  ggplot(aes(x = state, y = sales)) +
  geom_col(fill = "#2DC6D6") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by location(state)",
    subtitle = "",
    x = "State", # Override defaults for x and y
    y = "Revenue"
  )
```


## Challange 1.2
```{r, fig.width=10, fig.height=7}
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

bike_orderlines_joined_tbl <- orderlines_tbl %>%
        left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
        left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
        
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
 separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

sales_by_ly_tbl <- bike_orderlines_wrangled_cs_tbl %>%
  select(order_date, state, city, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(state, year) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))  

sales_by_ly_tbl %>%
  ggplot(aes(x = year, y = sales, fill = state)) +
  geom_col() +
  facet_wrap(~ state) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs( title = "Revenue by year and state",
        subtitle = "",
        fill = "State" # Changes the legend name
        )
```





# Challange 2

## Challange 2.1
Find "Seoul city" location and flight from Berlin to Seoul by using "rflights" package
```{r, fig.width=10, fig.height=7}
library("rflights")

#Find Seoul location
Seoul_find <- find_location("seoul", 
              location_types = c("city", "airport"))
    
lapply(Seoul_find, function(act_loc) {
  c(act_loc$name, act_loc$country$name, act_loc$region$name)
})

```

```{r, fig.width=10, fig.height=7}

#Find flight from Berlin to Seoul
Seoul_id <- find_location("seoul", "city")[[1]]$id
berlin_id <- find_location("berlin", "city")[[1]]$id
id <- c(Seoul_id, berlin_id)
id
```

```{r, fig.width=10, fig.height=7}
flights <- get_flights(fly_from = "berlin_de" , fly_to = "seoul_kr" , date_from = "09/10/2021",
  date_to = "19/10/2021" 
  )
  
length(flights)
head(t(sapply(flights, function(x) c(price = x$price, city_to = x$cityTo, duration = x$fly_duration, distance = x$distance))), n = 10)
```

## Challange 2.2

Database of competitor websites (https://www.rosebikes.de/)
```{r, fig.width=10, fig.height=7}
library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing

html_mtb <- read_html("https://www.rosebikes.de/fahrr%C3%A4der/mtb")

bike_tbl <- html_mtb %>%
  html_nodes(css = ".catalog-category-bikes__title-text") %>%
  html_text() %>% 
  stringr::str_replace_all(pattern = "\n", replacement = "") %>% 
  enframe(name = "No.", value = "bike_model")


price_tbl <- html_mtb %>%
  html_nodes(css = ".catalog-category-bikes__price-title") %>%
  html_text() %>%
  stringr::str_replace_all(pattern = "\nab ", replacement = "") %>%
  stringr::str_replace_all(pattern = "\n", replacement = "") %>%
  stringr::str_replace_all(pattern = "\200", replacement = "") %>%
  stringr::str_replace_all(pattern = ",00", replacement = "") %>%
  str_remove_all(pattern = "\\.")  %>%
  readr::parse_number() %>%
  enframe(name = "No.", value = "price")

left_join(bike_tbl,price_tbl)
```




# Challange 3
## Answer 1
```{r caluclation, eval=FALSE}
library(tidyverse)
library(vroom)
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

col_types <- list(
  id = col_character(),
  type = col_double(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "02_data_wrangling/assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl <- vroom(
  file       = "02_data_wrangling/patent_assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)



assignee_sl_tbl <- assignee_tbl %>%
  select(id, type, organization) %>%
  rename(
    assignee_id = id
  )

patent_sl_tbl <- patent_assignee_tbl %>%
  select(patent_id,assignee_id)


patent_assignee_joined_tbl <- assignee_sl_tbl %>%
  left_join(y = patent_sl_tbl, by = c("assignee_id" = "assignee_id")) %>%
  select(type,organization,patent_id) %>%
  filter(type == 2) %>%
  group_by(organization) %>%
  summarise(
    count = n()
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>%
  slice(1:10)

patent_assignee_joined_tbl
write_rds(patent_assignee_joined_tbl, "challange3_1.rds")

```

```{r result1}
library(readr)
library(data.table)
result1 <- read_rds("challange3_1.rds")
result1
```

# Challange 4

Last compiled: `r Sys.Date()`


