---
title: "Journal (reproducible report)"
author: "Pawin Traitrongsat"
date: "2020-11-28"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Challange 1

Last compiled: `r Sys.Date()`

## Challange 1.1
```{r, fig.width=10, fig.height=7}
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

bike_orderlines_joined_tbl <- orderlines_tbl %>%
        left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
        left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
        
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
 separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
  
bike_orderlines_wrangled_cs_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ",") 

sales_by_cs_tbl <- bike_orderlines_wrangled_cs_tbl %>%
  select(order_date, state, city, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(state, city) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))    
    
sales_by_cs_tbl %>%
  ggplot(aes(x = state, y = sales)) +
  geom_col(fill = "#2DC6D6") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by location(state)",
    subtitle = "",
    x = "State", # Override defaults for x and y
    y = "Revenue"
  )
```


## Challange 1.2
```{r, fig.width=10, fig.height=7}
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

bike_orderlines_joined_tbl <- orderlines_tbl %>%
        left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
        left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
        
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
 separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

sales_by_ly_tbl <- bike_orderlines_wrangled_cs_tbl %>%
  select(order_date, state, city, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(state, year) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))  

sales_by_ly_tbl %>%
  ggplot(aes(x = year, y = sales, fill = state)) +
  geom_col() +
  facet_wrap(~ state) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs( title = "Revenue by year and state",
        subtitle = "",
        fill = "State" # Changes the legend name
        )
```





# Challange 2

## Challange 2.1
Find "Seoul city" location and flight from Berlin to Seoul by using "rflights" package
```{r, fig.width=10, fig.height=7}
library("rflights")

#Find Seoul location
Seoul_find <- find_location("seoul", 
              location_types = c("city", "airport"))
    
lapply(Seoul_find, function(act_loc) {
  c(act_loc$name, act_loc$country$name, act_loc$region$name)
})

```

```{r, fig.width=10, fig.height=7}

#Find flight from Berlin to Seoul
Seoul_id <- find_location("seoul", "city")[[1]]$id
berlin_id <- find_location("berlin", "city")[[1]]$id
id <- c(Seoul_id, berlin_id)
id
```

```{r, fig.width=10, fig.height=7}
flights <- get_flights(fly_from = "berlin_de" , fly_to = "seoul_kr" , date_from = "09/10/2021",
  date_to = "19/10/2021" 
  )
  
length(flights)
head(t(sapply(flights, function(x) c(price = x$price, city_to = x$cityTo, duration = x$fly_duration, distance = x$distance))), n = 10)
```

## Challange 2.2

Database of competitor websites (https://www.rosebikes.de/)
```{r, fig.width=10, fig.height=7}
library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing

html_mtb <- read_html("https://www.rosebikes.de/fahrr%C3%A4der/mtb")

bike_tbl <- html_mtb %>%
  html_nodes(css = ".catalog-category-bikes__title-text") %>%
  html_text() %>% 
  stringr::str_replace_all(pattern = "\n", replacement = "") %>% 
  enframe(name = "No.", value = "bike_model")


price_tbl <- html_mtb %>%
  html_nodes(css = ".catalog-category-bikes__price-title") %>%
  html_text() %>%
  stringr::str_replace_all(pattern = "\nab ", replacement = "") %>%
  stringr::str_replace_all(pattern = "\n", replacement = "") %>%
  stringr::str_replace_all(pattern = "\200", replacement = "") %>%
  stringr::str_replace_all(pattern = ",00", replacement = "") %>%
  str_remove_all(pattern = "\\.")  %>%
  readr::parse_number() %>%
  enframe(name = "No.", value = "price")

left_join(bike_tbl,price_tbl)
```




# Challange 3
## Answer 1
```{r calculation, eval=FALSE}
library(tidyverse)
library(vroom)
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

col_types <- list(
  id = col_character(),
  type = col_double(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "02_data_wrangling/assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl <- vroom(
  file       = "02_data_wrangling/patent_assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)



assignee_sl_tbl <- assignee_tbl %>%
  select(id, type, organization) %>%
  rename(
    assignee_id = id
  )

patent_sl_tbl <- patent_assignee_tbl %>%
  select(patent_id,assignee_id)


patent_assignee_joined_tbl <- assignee_sl_tbl %>%
  left_join(y = patent_sl_tbl, by = c("assignee_id" = "assignee_id")) %>%
  select(type,organization,patent_id) %>%
  filter(type == 2) %>%
  group_by(organization) %>%
  summarise(
    count = n()
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>%
  slice(1:10)

patent_assignee_joined_tbl
write_rds(patent_assignee_joined_tbl, "challange3_1.rds")

```

```{r result1}
library(readr)
library(data.table)
result1 <- read_rds("challange3_1.rds")
result1
```

## Answer 2
```{r calculation2, eval=FALSE}
library(tidyverse)
library(vroom)
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

col_types <- list(
  id = col_character(),
  type = col_double(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl_2 <- vroom(
  file       = "02_data_wrangling/assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl_2 <- vroom(
  file       = "02_data_wrangling/patent_assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl_2 <- vroom(
  file       = "02_data_wrangling/patent.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

assignee_sl_tbl_2 <- assignee_tbl_2 %>%
  select(id, type, organization) %>%
  rename(
    assignee_id = id
  )

patent_assignee_sl_tbl_2 <- patent_assignee_tbl_2 %>%
  select(patent_id,assignee_id)

patent_sl_tbl_2 <- patent_tbl_2 %>%
  select(number, date) %>%
  rename(
    patent_id = number
  )

patent_assignee_joined_tbl_2 <- assignee_sl_tbl_2 %>%
  left_join(y = patent_assignee_sl_tbl2, by = c("assignee_id" = "assignee_id")) %>%
  left_join(y = patent_sl_tbl2, by = c("patent_id" = "patent_id")) %>%
  select(type,date,organization,patent_id) %>%
  filter(type == 2) %>%
  separate(col  = date,
           into = c("year", "month", "date"),
           sep  = "-", remove = FALSE) %>%
  mutate(
    year  = as.numeric(year)
  ) %>%
  filter(year == 2019) %>%
  group_by(organization) %>%
  summarise(
    count = n()
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>%
  slice(1:10)

patent_assignee_joined_tbl_2
write_rds(patent_assignee_joined_tbl_2, "challange3_2.rds")

```

```{r result2}
library(readr)
library(data.table)
answer2 <- read_rds("challange3_2.rds")
answer2
```

## Answer 3
```{r calculation3, eval=FALSE}
library(tidyverse)
library(vroom)
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

col_types <- list(
  id = col_character(),
  type = col_double(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl_3 <- vroom(
  file       = "02_data_wrangling/assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl_3 <- vroom(
  file       = "02_data_wrangling/patent_assignee.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)


col_types <- list(
  uuid = col_character(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_character(),
  sequence = col_double()
)

uspc_tbl_3 <- vroom(
  file       = "02_data_wrangling/uspc.tsv",
  delim      = "\t",
  col_names  = names(col_types),
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

assignee_sl_tbl_3 <- assignee_tbl_3 %>%
  select(id, type, organization) %>%
  rename(
    assignee_id = id
  )

patent_assignee_sl_tbl_3 <- patent_assignee_tbl_3 %>%
  select(patent_id,assignee_id)

uspc_sl_tbl_3 <- uspc_tbl_3 %>%
  select(patent_id, mainclass_id) 

patent_assignee_joined_tbl_3 <- assignee_sl_tbl_3 %>%
  left_join(y = patent_assignee_sl_tbl_3, by = c("assignee_id" = "assignee_id")) %>%
  select(type,organization,patent_id) %>%
  group_by(organization) %>%
  summarise(
    count = n()
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>%
  slice(1:10)
patent_assignee_joined_tbl_3

top_mainclass_tbl_3 <- assignee_sl_tbl_3 %>%
  left_join(y = patent_assignee_sl_tbl_3, by = c("assignee_id" = "assignee_id")) %>%
  left_join(y = uspc_sl_tbl_3, by = c("patent_id" = "patent_id")) %>%
  select(organization,mainclass_id) %>%
  filter(organization %in% c("International Business Machines Corporation", "Canon Kabushiki Kaisha","Samsung Electronics Co., Ltd.","General Electric Company","Kabushiki Kaisha Toshiba","Sony Corporation","Hitachi, Ltd.","Intel Corporation","Fujitsu Limited","NEC Corporation")) %>%
  group_by(mainclass_id) %>%
  summarise(
    count = n()
  ) %>%
  arrange(desc(count)) %>%
  ungroup() %>%
  slice(1:6) 

top_mainclass_tbl_3
write_rds(top_mainclass_tbl_3, "challange3_3.rds")

```

```{r result3}
library(readr)
library(data.table)
answers3 <- read_rds("challange3_3.rds")
answers3
```




# Challange 4

Last compiled: `r Sys.Date()`


